Is Vagueness Beneficial for Hearers? \protect \\ Evidence from Experiments

### 2016-09-25 papers/2016-Special-Issue/v-special-issue-2016.tex
got up to e2 graph, BUT NOT STATS

As expected, responses were faster and more accurate for vague than crisp instructions. Post hoc, we formulated some further hypotheses:

@@

Looking at Response Times, these two post-hoc hypotheses were confirmed, at Bonferroni-corrected significance levels:

@@

Looking at Error Rates, the two post-hoc hypotheses were confirmed as well, at Bonferroni-corrected significance levels:

@@

\subsubsection{Borderline responses} % E2
A generalized linear mixed model \cite{jaeger2008categorical} was fit to the data for selection of the borderline response, with task, vagueness and item as fixed effects, and with random slopes for task and vagueness and item over participants.  
The distribution of responses over the nearest match square, the borderline square, and the furthest match square are given in Fig, \ref{resultse2}. 
Participant grand mean percentage of borderline selections was $16.6\%$.  
\begin{APAenumerate}
	\item [(H5)] Participants were significantly more likely to choose the borderline option for vague instructions than for precise instructions (21.9\% vs 11.3\%, 
	($\beta=??$, $se=??$, $z=??$, $p<??$) % MG ADD STATS
	% $\beta=.79, se=.25, z=3.2, p<.01$).  
\end{APAenumerate}
Participants were also significantly more likely to choose the borderline square when the instruction used the numerical format rather than the verbal format (30.1\% vs 3.0\%, 
$\beta=??$, $se=??$, $z=??$, $p<??$) % MG ADD STATS
% $\beta=3.57, se=.26, z=13.6, p<.001$).

\begin{figure}[htbp]
\centering
\includegraphics[width=.49\textwidth]{images/response-time-sep-1.pdf}
\includegraphics[width=.49\textwidth]{images/histbd4-ggplot-version-1.pdf}
\caption{Experiment 2 results: response times and proportion of borderline cases}
\label{resultse2}
\end{figure}

>>>>

As expected, responses were faster and more accurate for vague than crisp instructions. Post hoc, we formulated some further hypotheses, which we tested using Bonferroni's correction for multiple comparisons:

@@

Looking at Response Times, these two post-hoc hypotheses were confirmed, at Bonferroni-corrected significance thresholds:

@@

Looking at Error Rates, the two post-hoc hypotheses were confirmed as well, at Bonferroni-corrected significance thresholds:

@@

\subsubsection{Borderline responses} % E2
A generalized linear mixed model \cite{jaeger2008categorical} was fit to the data for selection of the borderline response, with task, vagueness and item as fixed effects, and with random slopes for task and vagueness and item over participants.  
The distribution of responses over the nearest match square, the borderline square, and the furthest match square are given in Fig, \ref{resultse2}. 
Participant grand mean percentage of borderline selections was $16.6\%$.  
\begin{APAenumerate}
	\item [(H5)] Participants were significantly more likely to choose the borderline option for vague instructions than for precise instructions (21.9\% vs 11.3\%, 
	($\beta=??$, $se=??$, $z=??$, $p<??$) % MG ADD STATS
	% $\beta=.79, se=.25, z=3.2, p<.01$).  
\end{APAenumerate}
Participants were also significantly more likely to choose the borderline square when the instruction used the numerical format rather than the verbal format (30.1\% vs 3.0\%, 
$\beta=??$, $se=??$, $z=??$, $p<??$). % MG ADD STATS
% $\beta=3.57, se=.26, z=13.6, p<.001$).

\begin{figure}[htbp]
\centering
\includegraphics[width=.49\textwidth]{images/rtplote2.pdf}
\includegraphics[trim = 0mm -30mm 0mm 0mm, clip, width=.49\textwidth]{images/blplote2.pdf}
\caption{Experiment 2 results: response times and proportion of borderline cases}
\label{resultse2}
\end{figure}
